%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% One Page Resume
% Version 1.0 (14/10/19)
%
% Original author:
% Mariam Arab
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.5in,top=0.5in,right=0.5in,bottom=0.5in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Layla Arab}
\address{Contact: +1 (587) 716-7898 - layla.arab@ucalgary.ca}
\address{LinkedIn: linkedin.com/in/laylaarab}

\begin{document}
%   EDUCATION   %
\medskip
\begin{Entry}{Education}
{\bf University of Calgary, Schulich School of Engineering
} \hfill {\bf September 2017 - April 2022}
\\{\em Bsc. Software Engineering; Data Science Minor, GPA: 3.51}
\\ Activities and Societies: RoboGals, Eco-Car Team, Leadership Program Member, Engineering Mentor
\end{Entry}

%  WORK EXPERIENCE   %
 \medskip
\begin{Entry}{Experience}
{\bf Eco Car Software Executive } \hfill {\bf September 2019 - Present}
\\{\em Schulich School of Engineering}
\\ Founding member of Schulich's Shell Eco-marathon team.
\begin{itemize} \itemsep -5pt
  \item Create embedded systems for the team’s Eco Car.
  \item Coordinate with other members to develop project timelines.
  \item Recruit members from different fields to promote more diverse opinions.
\end{itemize}

{\bf Vice President of Sponsorships} \hfill {\bf February 2020 - Present}
\\{\em RoboGals UCalgary}
% \\ Promote STEM fields to girls. Responsible for securing funds from new sponsors.
\\ Secure funds from sponsors and enlist RoboGals for club awards. 
\begin{itemize} \itemsep -5pt
  \item Employ speakers to give motivational talks at workshops.
  \item Enlist RoboGals for sponsorships and award applications.
\end{itemize}
\end{Entry}

% ADDITIONAL EXPERIENCE %
\medskip
\begin{Entry}{Additional Experience}
{\bf Volunteer Coordinator} \hfill {\bf April 2019 - February 2020}
\\{\em RoboGals UCalgary}
\\ Promote STEM fields to girls. Responsible for recruiting and managing the club's volunteer base.
\begin{itemize} \itemsep -5pt
  \item Manage logistics to ensure workshop success.
  \item Develop more efficient volunteer sign-up systems.
  \item Create and manage Facebook page to advertise workshops.
\end{itemize}

{\bf Volunteer} \hfill {\bf September 2017 - April 2019}
\\{\em RoboGals UCalgary}
\begin{itemize} \itemsep -5pt
  \item Volunteer at workshops to encourage young girls to pursue STEM fields
  \item Encourage groupwork and procedural techniques to solve the problem at hand
\end{itemize}

{\bf International Student Mentor} \hfill {\bf September 2018 - May 2019}
\\{\em Schulich Mentorship Program}
\\ Mentored two international students through the first year of their degree
\begin{itemize} \itemsep -5pt
    \item Set up regular meetings with mentees to ensure integration
    \item Provide additional support where needed
\end{itemize}

{\bf Leadership Program Member} \hfill {\bf September 2018 - May 2019}
\\{\em Schulich Leadership Program}
\\  Learn skills necessary for engineers in industry beyond coursework. 
\begin{itemize} \itemsep -5pt
  \item Develop self-awareness, communication, and time management skills
  \item Network with other program attendees
\end{itemize}
\end{Entry}

\clearpage
%   SELECT PROJECTS   %
 \medskip
\begin{Entry}{Select Projects}
{\bf Weasel Beagle} \hfill {\bf Fall 2019}
\\ Implemented using a MEAN stack and custom REST API, WeaselBeagle is a pet adoption website that services shelters, adopters, as well as vets and trainers. 

{\bf Rental Property Management System} \hfill {\bf Fall 2019}
\\ Uses Vaadin, a Java framework built on Spring Boot. The DocuSign API is used to implement contract signing. The system services landlords and renters by allowing the registration and rental of properties.

{\bf ScrapCycle} \hfill {\bf November 2019}
\\{\em Code the Change Hackathon, 2\textsuperscript{nd} place}
\\ ScrapCycle is a material exchange system for corporations. The platform allows businesses to advertise excess raw materials on the system. This reduces business waste. Uses the Vaadin framework.

{\bf Client-server Toolshop Application} \hfill {\bf Winter 2019}
\\ A client-server application built on Java with a JFrame frontend. Businesses can manage their tool inventory, and can set up automatic tool restocking.
\end{Entry}

% TECHNICAL SKILLS %
\medskip

\begin{Entry}{Technical Skills}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages \ & Java, C, C++, JavaScript, Node.js, R, Python, MySQL, MongoDB, Elastic \\
Frameworks \ & Angular, Vaadin, Spring Boot, React, Spark, Pandas   \\
DevOps \ & Docker, Azure, AWS, Google Cloud \\
\end{tabular}
\end{Entry}

%   ACHIEVEMENTS   %
 \medskip
\begin{Entry}{Achievements and Scholarships}

{\bf Jason Lang Scholarship, Schulich School of Engineering } \hfill {\bf 2019}

{\bf Dean’s List, Schulich School of Engineering } \hfill {\bf 2018}

{\bf Margaret and Ted Newall Bursary}  \hfill {\bf 2017}

{\bf Duke of Edinburgh International Silver Awards }  \hfill {\bf 2016}

\end{Entry}

\end{document}
